---
title: "vaccine_delay_fits"
author: "Weizhi LIU"
date: "2022-11-07"
output: pdf_document
---
## Some initial settings and version check


```{r}
source("global_util.R")

version_check("sircovid", "0.13.15")
version_check("spimalot", "0.7.11")
```

## Specify the MCMC parameters
```{r}
date <- "2021-09-13"
model_type <- "BB" 

#Some data streams are unreliable for the last few days. Define how many days here.
trim_deaths <- 4
trim_pillar2 <- 5

## MCMC control (only applies if short_run = FALSE)
burnin <- 500
n_mcmc <- 1500
chains <- 4
kernel_scaling <- 0.2
```

spim_check_region checks if the target region is a valid NHS region in dataset.
```{r}
#Checks current region is valid
region <- spimalot::spim_check_region(region, FALSE)
```


spim_fit_pars_load loads the parameters. This function loads the data in _parameters_ folder and conducts some pre-processing.
```{r}
#Checks and assembles all the outputs from vaccine_delay_parameter_fits task
#Output pars is a list containing:
#info - the loaded info.csv
#prior - the loaded prior.csv
#proposal - the loaded proposal.csv
#transform - the functions in transform.R
#raw - exact output of first 3 csvs, without any treatment
#base - the baseline.rds object
#mcmc - some sort of initialisation object built from the above to pass to the mcmc
pars <- spimalot::spim_fit_pars_load("parameters", region, "central",
                                     kernel_scaling)

restart_date <- readRDS("parameters/base.rds")[[region[[1]]]]$restart_date
```

This command sets the parameters for the MCMC. This function firstly set up parameters for the parallel computation by invoking _spim_control_parallel_ function. Then, invokes _mcstate::pmcmc_control_ [(this package)](https://github.com/mrc-ide/mcstate/blob/master/R/pmcmc_control.R) which verify the availability of the MCMC parameters and set MCMC modes.
```{r}
#This sets up a lot of pmcmc controls, checks iterations are compatible etc.
control <- spimalot::spim_control(
  short_run, chains, deterministic, date_restart = restart_date,
  n_mcmc = n_mcmc, burnin = burnin)
```
Load and trim data
```{r}
data_rtm <- read_csv("data/rtm.csv")
data_serology <- read_csv("data/serology.csv")

#This trims off dates and columns we don't want
library(dplyr)
data <- spim_data(
  date, region, model_type, data_rtm, data_serology,
  trim_deaths, trim_pillar2,
  full_data = FALSE)

#Some more particle filter setup, this object can then be "run" below
filter <- spimalot::spim_particle_filter(data, pars$mcmc,
                                         control$particle_filter,
                                         deterministic)
```

This function runs the MCMC from [_pmcmc_](https://github.com/mrc-ide/mcstate/blob/master/R/pmcmc.R) which creates a _R6class_ object. The object invokes _run()_ function to run the chain
```{r}
## This bit takes ages, of course
samples <- spimalot::spim_fit_run(pars, filter, control$pmcmc)
```


```{r}
## This is the data set including series that we do not fit to, and
## with the full series of carehomes deaths.
data_full <- spim_data(
  date, region, model_type, data_rtm,
  data_serology, trim_deaths, trim_pillar2,
  full_data = TRUE)
```


(UNSURE) Fit the model with simulated samples
```{r}
## This is new, and used only in sorting out the final outputs. Some
## explanation would be useful.
data_inputs <- list(rtm = data_rtm,
                    full = data_full,
                    fitted = data)

dat <- spimalot::spim_fit_process(samples, pars, data_inputs)
dat$fit$simulate$n_doses <-
simulate_calculate_vaccination_new(dat$fit$simulate$state, pars, region)
```


This section creates output directory and save the output data and plots.
```{r}
dir.create("outputs", FALSE, TRUE)
saveRDS(dat$fit, "outputs/fit.rds")
saveRDS(dat$restart, "outputs/restart.rds")

message("Creating plots")
write_pdf(
  "outputs/pmcmc_traceplots.pdf",
  spimalot::spim_plot_fit_traces(dat$fit$samples),
  width = 16, height = 9)
```







